How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

\begin{abstract}
Using a Cauchy integral formulation of the boundary integral equations, we numerically simulation the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow. The bodies comprising the porous medium are resolved individually and erode under the action of surface shear stress. In particular, changes in the morphology of individual bodies are resolved in detail, and these microscopic changes give rise to larger-scale features in the medium such as channelization. The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies. Armed with these methods, we observe anisotropy 
\end{abstract}
\maketitle

impinging intervening interal

@@

Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work). The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations (cite new paper with Shang).

% Need to include descriptor 'high-fidelity' for our simulation.

@@

% NOTE: THIS SECTION HAS BEEN PLAGIARIZED FROM JFM 2020
% SO WE NEED TO PARAPHRASE IT
%\begin{comment}
%-----------------------------------------------------------------------------------------------%
\section{Governing Equations}
\label{sec:formulation}
%-----------------------------------------------------------------------------------------------%

@@

%\vsp{2} \nick{Finished rewording up to here} \vsp{2}
%
%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
%corresponding deformation tensor, pressure, and vorticity at $\xx \in
%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
%To compute the deformation tensor for $\xx \in \gamma$, we include the
%jump term
%\begin{align}
%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
%    \begin{array}{cc}
%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
%    \end{array}
%  \right].
%  \label{eqn:deformationJump}
%\end{align}
%Finally, the deformation tensor, pressure, and vorticity due to the
%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
%computed the deformation tensor on $\gamma$, the shear stress is
%computed using equation~\eqref{eqn:shearStress}.

@@

%\end{comment}

>>>>

\begin{abstract}
Using a Cauchy integral formulation of the boundary integral equations, we simulate the erosion a porous medium comprised of $O(100)$ solid bodies embedded in a Stokes flow. The grains of the medium are resolved individually and erode under the action of surface shear stress. In particular, detailed changes in grain morphology are resolved, and these microscopic changes give rise to larger-scale features in the medium such as channelization. The Cauchy-integral and barycentric quadrature formulas allows us to resolve configurations of tightly packed and nearly contacting bodies. We observe substantial anisotropy to develop over the course of erosion; that is, the configurations that result from erosion generally permit flow in the longitudinal direction more easily than in the transverse direction by a factor of roughly five.  \\
Tie it to alternate hypothesis in groundwater.
\end{abstract}
\maketitle

@@

Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of order hundreds of solid bodies (please see \cite{Mitchell2016} for related work). The recent incorporation of barycentric interpolation methods permits simulation of tightly packed configurations \cite{chiu2020viscous}

% Can include descriptor 'high-fidelity' for our simulation.

@@

%-----------------------------------------------------------------------------------------------%
\section{Governing Equations}
\label{sec:formulation}
%-----------------------------------------------------------------------------------------------%

@@

%
%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
%corresponding deformation tensor, pressure, and vorticity at $\xx \in
%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
%To compute the deformation tensor for $\xx \in \gamma$, we include the
%jump term
%\begin{align}
%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
%    \begin{array}{cc}
%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
%    \end{array}
%  \right].
%  \label{eqn:deformationJump}
%\end{align}
%Finally, the deformation tensor, pressure, and vorticity due to the
%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
%computed the deformation tensor on $\gamma$, the shear stress is
%computed using equation~\eqref{eqn:shearStress}.

@@
